The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-24 paper.tex
update

  A crucial component in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The pyFC randomly generates dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$ that is clumpy and porous.
  The random scalar field obeys the log-normal probability distribution\
  %the log-normal probability distribution \citep{Berkhuijsen2008}\
  with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f_{\text{clumpy}}(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\

@@

@@

\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                                    & Description                               & Value                                \\ \midrule
{\bf Static stellar potential }\citep{velocity-dispersion-MW}&                                           &                                      \\
$\sigma_{\text{bulge}}$                                      & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                \\
$\rho_{\text{bulge}}^{\text{peak}}$                          & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ \\ \hline
{\bf Static dark halo potential }\citep{Johnston1995}        &                                           &                                      \\
$v_{\text{halo}}$                                            &                                           & 131.5 km$\cdot$s$^{-1}$              \\
$d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \hline
{\bf Isothermal disk }\citep{peak-ism-density}               &                                           &                                      \\
$z_{0}$                                                      & Scale height of disk                      & 100 pc                               \\
$T_{\text{\text{isoDisk}}}$                                  & Temperature of disk                       & $10^{3}$ K                           \\
$\rho_{\text{isoDisk}}^{\text{peak}}$                        & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         \\ \hline
{\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\ \hline
{\bf Clumpy disk }\citep{Wagner2012}                         &                                           &                                      \\
$T_{\text{\text{c}}}$                                        & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   \\
$k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
$\mu_{\text{clumpy}}$                                        & Mean of scalar field                      & 1.0                                  \\
$\sigma_{\text{clumpy}}$                                     & Dispersion of scalar field                & 1.7                                  \\ % RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES Wagner (2011)
$\beta$                                                      & Power law index                           & -5/3                                 \\ \midrule
\end{tabular}
\end{table*}

>>>>

   % The dispersion:
   %   2010-Comparing the statistics of interstellar turbulence in simulations and observations
   %   2011-RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES

  A crucial component in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.\

  The pyFC randomly generates dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f_{\text{clumpy}}(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\

@@

  The porosity of the warm phase arises by imposing an upper temperature cutoff for the\
  existence of clouds at $T_{\text{crit}} = 10^{4}$ K, beyond which clouds
  are deemed thermally unstable.

@@

\begin{table*}[t]
\raggedright
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                                    & Description                               & Value                                \\ \midrule
{\bf Static stellar potential }\citep{velocity-dispersion-MW}&                                           &                                      \\
$\sigma_{\text{bulge}}$                                      & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                \\
$\rho_{\text{bulge}}^{\text{peak}}$                          & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ \\ \hline
{\bf Static dark halo potential }\citep{Johnston1995}        &                                           &                                      \\
$v_{\text{halo}}$                                            &                                           & 131.5 km$\cdot$s$^{-1}$              \\
$d_{\text{h}}$                                               & Core radius                               & 12 kpc                               \\ \hline
{\bf Atmosphere }\citep{temperature-MW}                      &                                           &                                      \\
$T_{\text{\text{atmp}}}$                                     & Temperature of atmosphere                 & $10^{6}$ K                           \\ \hline
{\bf Isothermal disk }\citep{peak-ism-density}               &                                           &                                      \\
$z_{0}$                                                      & Scale height of disk                      & 100 pc                               \\
$T_{\text{\text{isoDisk}}}$                                  & Temperature of disk                       & $10^{3}$ K                           \\
$\rho_{\text{isoDisk}}^{\text{peak}}$                        & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         \\ \hline
{\bf Clumpy disk }\citep{Wagner2012}                         &                                           &                                      \\
$T_{\text{\text{c}}}$                                        & Critical temperature of warm atomic phase & $3\times 10^{4}$ K                   \\
$\dagger k_{\text{min}}$                                             & Cutoff wave number                        & 375.0                                \\
$\mu_{\text{clumpy}}$                                        & Mean of scalar field                      & 1.0                                  \\
$\sigma_{\text{clumpy}}$                                     & Dispersion of scalar field                & 1.7                                  \\ % RELATIVISTIC JET FEEDBACK IN EVOLVING GALAXIES Wagner (2011)
$\beta$                                                      & Power law index                           & -5/3                                 \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \small
      \item  $\dagger k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
    \end{tablenotes}
\end{table*}
